---
title: "DS_Capstone VM"
author: "Veeksha Madhu"
date: "3/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
d <- read.csv("WA state_ccc2.csv", header=TRUE)
colnames(d) <- as.character(unlist(d[1,]))
da = d[-1, ]
statewide = da[nrow(da),]
data = da[-nrow(da),]
dat <- data[,2:17]
chars <- sapply(dat, is.character)
dat[ , chars] <- as.data.frame(apply(dat[ , chars], 2, as.numeric))
data[,2:17] <- dat

head(data)

```
```{r}
infants <- data[, 1:5]
head(infants)

toddler <- data[c(-2,-3,-4,-5,-10:-18)]
head(toddler)

preschool <- data[c(-2:-9,-14:-18)]
head(preschool)

schoolage <- data[c(-2:-13)]
head(schoolage)
```

```{r}
library("vioplot")
x1 <- infants$`Median Rate`
x2 <- toddler$`Median Rate`
x3 <- preschool$`Median Rate`
x4 <- schoolage$`Median Rate`
vioplot(x1, x2, x3, x4, names=c("Infants", "Toddlers", "Pre-school", 'School Age'),
   col=c("red","yellow","blue", "green"), ylab = "Dollars $")
title("Median rates across all four age groups")

```

```{r}
y1 <- infants$`Subsidy Rate`
y2 <- toddler$`Subsidy Rate`
y3 <- preschool$`Subsidy Rate`
y4 <- schoolage$`Subsidy Rate`

vioplot(y1,y2,y3,y4, names=c("Infants","Toddlers","Preschool", "School Age"), col=c("red","yellow","blue", "green"))
```

Looking at Infants data
```{r}
infantsnew <- infants[,-1]
library("MVA")
attach(infantsnew)

bvbox(cbind(`Median Rate`,`Subsidy Rate`),ylab = "Subsity Rate",
  xlab = "Median Rate")
```

Lasso Regression
```{r}
library(glmnet)
n <- 100
x1<- runif(n,0,1)
x2<- runif(n,0,1)
x3<- runif(n,0,1)
n <- 100

coefs.lasso <- matrix(NA,nrow=1000,ncol=4)
for(i in 1:1000){
  set.seed(i) #set the seed so that we all generate the same set of random samples
  error <- rnorm(n,mean=0,sd=0.1)
  y <- 1+2*x1+3*x2+0*x3+error
  result.lasso <- cv.glmnet(x=cbind(x1,x2,x3), y=y, family="gaussian",alpha=1)
  coefs.lasso[i,] <- as.vector(coef(result.lasso,s=result.lasso$lambda.min))}

coefs.lasso[i,]
```

VIF model
```{r}
attach(infantsnew)
library(car)

vif(lm(`Median Rate`~.,data=infantsnew[,-2]))
```
AIC 
```{r}
fit <- lm(`Median Rate`~.,data=infantsnew)
result.AIC <- step(fit, k=2,direction="both",trace=FALSE)
summary(result.AIC)
```

BIC
```{r}
result.BIC <- step(fit, k=log(dim(infantsnew)[2]),direction="both",trace=FALSE)
summary(result.BIC)
```

2 sample-test and F test for median rates for infants and toddlers
```{r}
t.test(x1, x2)
var.test(x1, x2,  alternative = "two.sided")
```

2 sample-test and F test for median rates for infants and preschoolers
```{r}
t.test(x1, x3)
var.test(x1, x3,  alternative = "two.sided")
```

2 sample-test and F test for median rates for infants and school age children
```{r}
t.test(x1, x4)
var.test(x1, x4,  alternative = "two.sided")
```

2 sample-test and F test for subsidy rates for toddlers and preschoolers
```{r}
t.test(y2, y3)
var.test(y2, y3,  alternative = "two.sided")
```

2 sample-test and F test for subsidy rates for infants and school age children
```{r}
t.test(y1, y4)
var.test(y1, y4,  alternative = "two.sided")
```

```{r}
library("multcompView")
datarev <- read.csv("WA state_ccc 2rev.csv", header=TRUE)
datarevclean <- subset (datarev, select = -1)
anova <- aov(datarev$Subsidy.Rate ~ datarev$Age.Group)
TukeyHSD(anova, conf.level=.95)
```

```{r}
anova1 <- aov(datarev$Median.Rate ~ datarev$Age.Group)
TukeyHSD(anova1, conf.level=.95)
``` 